Appendix to 'Detecting social information in a dense database of infants’ natural

### 2022-01-04 paper/preprint/appendix.Rmd
minor edits to appendix
(but missing the thresholded detections data file!)

```{r}
load(here::here("data","preprocessed_data_2021","gold_sample_from_bbs_2021_all_detections_all_thresholds.RData"))

@@

```{r}
hand_cruise <- lmer(prop_hands ~ age * cruise + (1 | child_id), 
     data=face_hand_by_age_milestones)
summary(hand_cruise) 
# cruise+*, age*cruise-.
tab_model(hand_cruise, show.re.var=F, dv.labels = "Proportion of Hands")
```

@@

Walking - only a marginal positive effect on the proportion of hands ($\beta = 0.09$, $p=0.052$).

>>>>

```{r}
# file not found - name changed?
load(here::here("data","preprocessed_data_2021","gold_sample_from_bbs_2021_all_detections_all_thresholds.RData"))

@@

```{r}
hand_cruise <- lmer(prop_hands ~ age * cruise + (1 | child_id), 
     data=face_hand_by_age_milestones)
summary(hand_cruise) 
# cruise+*, age*cruise-.
tab_model(hand_cruise, show.re.var=F, dv.labels = "Proportion of Hands") # show.obs=F
```

@@

As children became able to walk, they saw marginally more hands ($\beta = 0.09$, $p=0.052$).
